---
title: "Face Judgement & Survey Data Analysis — Pre-Registered Pipeline"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(broom.mixed)
knitr::opts_chunk$set(echo = TRUE)
```

## Before knitting

Re-export the latest data from the database (the CSVs below are gitignored, so
this must be run locally first):

```
python3 -c "from export_participant_data import export_clean_data; export_clean_data()"
```

## Overview

This pipeline implements the analysis plan in `Isaac pre-registration draft.txt`,
run on the **9 pilot participants collected so far** (ids 7-10 and 20-24) out of
the planned 600. All 9 happen to be in the `professional` advice condition — no
`emotional` or `intelligence`-condition data exists yet. That means:

- The **primary confirmatory test** (fit within the professional condition) can
  be run on the full pilot sample.
- The **domain-specificity test** (`Condition × FaceAge × CreativePerceptions`)
  and the **mechanism-probe model** (fit within the intelligence condition)
  can't be fit yet — there's no other-condition data to contrast against. Their
  formulas are documented below, ready to run once those conditions have data.
- With n=9 (vs. the planned n=600), expect convergence warnings, singular fits,
  and wide/unstable estimates throughout. **Nothing here is a meaningful test of
  H1/H2 yet** — this is a pipeline correctness check on pilot data, not a result.

## Step 1: Merge survey data with face judgement data

```{r read-data}
survey_data <- read_csv("/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/survey_data.csv", show_col_types = FALSE)
face_trials <- read_csv("/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/face_judgement_trials.csv", show_col_types = FALSE)
```

Extract the face number from the stimulus path (e.g. `".../13 copy.jpg"` -> `"13"`).

```{r extract-face-num}
face_trials <- face_trials %>%
  mutate(face_num = str_extract(stimulus, "(?<=Faces/)\\d+(?= copy\\.jpg)"))

stopifnot(!any(is.na(face_trials$face_num)))
```

Each participant sees 60 unique faces and 10 of those are shown twice (70 trials
total). Within each participant, label the first showing of a face `face_<num>`
and the second showing `face_<num>_repeat`, then pivot to one row per participant.

```{r pivot-wide}
face_wide <- face_trials %>%
  arrange(participant_id, trial_index) %>%
  group_by(participant_id, face_num) %>%
  mutate(occurrence = row_number()) %>%
  ungroup() %>%
  mutate(col_name = if_else(
    occurrence == 1,
    paste0("face_", face_num),
    paste0("face_", face_num, "_repeat")
  )) %>%
  select(participant_id, col_name, rating) %>%
  pivot_wider(names_from = col_name, values_from = rating)
```

Merge onto the survey data, one row per participant.

```{r merge}
merged_data <- survey_data %>%
  left_join(face_wide, by = "participant_id")
```

Sanity check: every participant should contribute 70 face columns (60 unique +
10 repeats), and row count should match `survey_data`.

```{r check-merge}
face_cols <- merged_data %>% select(starts_with("face_")) %>% names()
length(face_cols)        # expect 70
nrow(merged_data) == nrow(survey_data)
```

### Reconcile renamed survey columns

The survey instruments were renamed partway through data collection (commit
`bc3bed8`): `survey3`->`kaiSurvey`, `survey4`->`big5Personality`,
`survey5`->`creativePerceptions`, `survey6`->`workHabits`, and the original
`survey_*` demographics fields -> `demographics_*`. Question numbering/order
was unchanged, only the prefix. Participants 7-10 (before the rename) have
their answers under the old prefix; participants 20-24 (after) have them under
the new prefix — coalesce each old/new pair into the new (current) column name
and drop the old one. (Fields added *after* the rename — Three Good Lives, and
the political/education/SES demographics items — simply don't exist for
participants 7-10; they'll be `NA` for those 4 participants throughout.)

```{r reconcile-renamed-columns}
demo_suffixes <- c("age", "comments", "estimatedPerformance", "gender",
                    "interruption", "issues", "participatedBefore", "race",
                    "seriousness", "sex", "strategies")

old_to_new <- c(
  setNames(paste0("kaiSurvey_Q", 1:33), paste0("survey3_Q", 1:33)),
  setNames(paste0("big5Personality_Q", 1:10), paste0("survey4_Q", 1:10)),
  setNames(paste0("creativePerceptions_Q", 1:11), paste0("survey5_Q", 1:11)),
  setNames(c(paste0("workHabits_Q", 1:12), "workHabits_jobDescription"),
           c(paste0("survey6_Q", 1:12), "survey6_jobDescription")),
  setNames(paste0("demographics_", demo_suffixes), paste0("survey_", demo_suffixes))
)

for (old_col in names(old_to_new)) {
  new_col <- old_to_new[[old_col]]
  merged_data[[new_col]] <- coalesce(merged_data[[new_col]], merged_data[[old_col]])
}

merged_data <- merged_data %>% select(-all_of(names(old_to_new)))
```

```{r write-merged}
write_csv(merged_data, "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/merged_survey_face_data.csv")
```

## Step 2: Filter to the 9 pilot participants (7, 8, 9, 10, 20, 21, 22, 23, 24)

```{r filter}
pilot_ids <- c(7, 8, 9, 10, 20, 21, 22, 23, 24)

filtered_data <- merged_data %>%
  filter(participant_id %in% pilot_ids)

filtered_data %>% select(participant_id, condition)
```

Data is kept anonymized; only `participant_id` is used throughout, no name
mapping is applied.

```{r write-filtered}
write_csv(filtered_data, "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/filtered_data_9participants.csv")
```

## Step 3: Within-participant test-retest reliability

Pre-registered exclusion criterion #1. For each participant, pair up their
first and repeat rating on each of the 10 repeated faces, then compute one
Pearson correlation per participant across those 10 pairs.

```{r face-long}
face_long <- filtered_data %>%
  select(participant_id, matches("^face_\\d+$")) %>%
  pivot_longer(
    cols = matches("^face_\\d+$"),
    names_to = "face_num",
    values_to = "rating"
  ) %>%
  mutate(face_num = str_remove(face_num, "^face_"))
```

```{r repeat-pairs}
repeat_face_nums <- c(1, 2, 4, 5, 6, 7, 9, 15, 24, 79)

repeat_pairs <- filtered_data %>%
  select(
    participant_id,
    all_of(paste0("face_", repeat_face_nums)),
    all_of(paste0("face_", repeat_face_nums, "_repeat"))
  ) %>%
  pivot_longer(
    cols = -participant_id,
    names_to = c("face_num", "rep"),
    names_pattern = "^face_(\\d+)(_repeat)?$",
    values_to = "rating"
  ) %>%
  mutate(rep = if_else(rep == "_repeat", "rating2", "rating1")) %>%
  pivot_wider(names_from = rep, values_from = rating)
```

```{r reliability}
reliability <- repeat_pairs %>%
  group_by(participant_id) %>%
  summarise(
    n_pairs = n(),
    pearson_r = cor(rating1, rating2, method = "pearson"),
    .groups = "drop"
  )

reliability
```

```{r write-reliability}
write_csv(
  reliability,
  "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/within_participant_reliability.csv"
)
```

## Step 4: Visualizing agreement across participants

Every participant rates all 70 face presentations (60 unique faces + 10 shown
twice), so plotting all 70 ratings per participant on the same face axis shows
directly how much participants agree with each other on any given face — tight
vertical clusters mean strong agreement, wide spread means participants see
that face very differently. Faces are sorted by their mean rating (low to
high) and each participant gets one consistent color across the whole plot; a
black tick marks the per-face mean.

```{r agreement-plot-data}
agreement_data <- face_trials %>%
  filter(participant_id %in% pilot_ids) %>%
  select(participant_id, face_num, rating)

face_order <- agreement_data %>%
  group_by(face_num) %>%
  summarise(mean_rating = mean(rating, na.rm = TRUE), .groups = "drop") %>%
  arrange(mean_rating) %>%
  pull(face_num)

agreement_data <- agreement_data %>%
  mutate(
    face_num = factor(face_num, levels = face_order),
    participant_id = factor(participant_id)
  )

face_means <- agreement_data %>%
  group_by(face_num) %>%
  summarise(mean_rating = mean(rating, na.rm = TRUE), .groups = "drop")
```

```{r agreement-plot, fig.width=8, fig.height=13}
agreement_plot <- ggplot(agreement_data, aes(x = rating, y = face_num, color = participant_id)) +
  geom_jitter(height = 0.15, width = 0, size = 2, alpha = 0.85) +
  geom_point(
    data = face_means, aes(x = mean_rating, y = face_num),
    inherit.aes = FALSE, shape = "|", size = 5, color = "black"
  ) +
  labs(
    x = "Rating (0-100 slider)",
    y = "Face (sorted by mean rating, low -> high)",
    color = "Participant",
    title = "Face ratings by participant (9 participants x 70 presentations)",
    subtitle = "Black tick = mean rating for that face"
  ) +
  theme_bw() +
  theme(axis.text.y = element_text(size = 6))

agreement_plot
```

```{r write-agreement-plot}
ggsave(
  "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/face_ratings_by_participant.png",
  agreement_plot, width = 8, height = 13, dpi = 150
)
```

## Step 5: Straight-lining check

Pre-registered exclusion criterion #5: identical ratings on more than 90% of
trials. Computed over each participant's 60 first-presentation trials (the
modal rating's share of those 60).

```{r straightlining}
straightlining <- face_long %>%
  group_by(participant_id, rating) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(participant_id) %>%
  summarise(
    modal_rating_share = max(n) / sum(n),
    .groups = "drop"
  )

straightlining
```

## Step 6: Exclusion criteria

Applying all 5 pre-registered exclusion criteria, blind to condition (all 9
happen to be `professional` here, so this is moot for this batch but kept
general):

1. Test-retest reliability r <= 0 (chance-level or inverted consistency).
   A stricter sensitivity cutoff of r < .30 is also flagged separately, per the
   pre-registration's sensitivity analysis.
2. Failure of the attention/bot check. **Not computable from stored data** —
   both the attrition free-text check and the captcha word-match are validated
   client-side (`frontend/src/js/utils.js`, `attritionAnswer`/`captchaAnswer`
   rules) and block form submission until answered correctly. Every participant
   in the database already passed by construction, so this always evaluates to
   FALSE here rather than being a meaningful check on this data. (Participants
   7-10 additionally predate the captcha page — only the attrition check
   existed for them.)
3. Self-reported prior completion of the study (`participatedBefore == "Yes"`).
4. Self-reported attentiveness/distractedness. The demographics form only has
   one relevant item, `seriousness` (1 = very distracted, 100 = very focused) —
   there's no separate distractedness question, so the two pre-registered
   criteria collapse to one check: `seriousness < 50`.
5. Straight-lining: modal rating share > 90% of the 60 first-presentation trials.

```{r exclusions}
exclusions <- filtered_data %>%
  select(participant_id, participatedBefore = demographics_participatedBefore,
         seriousness = demographics_seriousness) %>%
  left_join(reliability %>% select(participant_id, pearson_r), by = "participant_id") %>%
  left_join(straightlining, by = "participant_id") %>%
  mutate(
    reliability_leq_0 = pearson_r <= 0,
    reliability_sensitivity_lt_030 = pearson_r < 0.30,
    participated_before = participatedBefore == "Yes",
    low_seriousness = seriousness < 50,
    straightlining = modal_rating_share > 0.90,
    bot_or_attention_check_fail = FALSE,  # not computable — see note above
    excluded = reliability_leq_0 | participated_before | low_seriousness |
      straightlining | bot_or_attention_check_fail
  )

exclusions %>%
  select(participant_id, pearson_r, reliability_leq_0, reliability_sensitivity_lt_030,
         participated_before, low_seriousness, straightlining,
         bot_or_attention_check_fail, excluded)
```

```{r write-exclusions}
write_csv(exclusions, "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/exclusions.csv")
```

```{r apply-exclusions}
n_excluded <- sum(exclusions$excluded)
cat(n_excluded, "of", nrow(exclusions), "participants excluded.\n")

analysis_sample <- filtered_data %>%
  filter(participant_id %in% (exclusions %>% filter(!excluded) %>% pull(participant_id)))
```

## Step 7: Big Five (TIPI) scoring

`big5Personality_Q1`-`Q10` is the standard 10-item TIPI (confirmed against
`frontend/src/html/big5-personality.html`), 7-point scale (1 = Completely
Disagree ... 7 = Completely Agree), standard item order. Reverse items are the
even-numbered ones; reverse formula is `8 - x` (min + max = 8 on a 1-7 scale).
Each trait score is the mean of its 2 items after reversing the reverse one.

```{r big5-scoring}
# Stored as text labels with the numeric value trailing in parens, e.g.
# "Somewhat Agree (5)" -- extract the number rather than assuming it's numeric.
extract_paren_num <- function(x) as.numeric(str_extract(x, "(?<=\\()\\d+(?=\\)$)"))

b5 <- analysis_sample %>%
  select(participant_id, matches("^big5Personality_Q\\d+$")) %>%
  mutate(across(matches("^big5Personality_Q\\d+$"), extract_paren_num))

b5_scored <- b5 %>%
  mutate(
    Extraversion       = rowMeans(cbind(big5Personality_Q1, 8 - big5Personality_Q6), na.rm = TRUE),
    Agreeableness      = rowMeans(cbind(8 - big5Personality_Q2, big5Personality_Q7), na.rm = TRUE),
    Conscientiousness  = rowMeans(cbind(big5Personality_Q3, 8 - big5Personality_Q8), na.rm = TRUE),
    EmotionalStability = rowMeans(cbind(8 - big5Personality_Q4, big5Personality_Q9), na.rm = TRUE),
    Openness           = rowMeans(cbind(big5Personality_Q5, 8 - big5Personality_Q10), na.rm = TRUE)
  ) %>%
  select(participant_id, Extraversion, Agreeableness, Conscientiousness,
         EmotionalStability, Openness)

b5_scored
```

## Step 8: Likert recoding and reverse-scoring for the other surveys

KAI uses a 4-point scale (Very Hard=1 ... Very Easy=4); Creative Perceptions
and Work Habits use a 5-point agree/disagree scale (Strongly Disagree=1 ...
Strongly Agree=5).

**Work Habits reverse item — corrected**: checking the actual item wording in
`frontend/src/html/work-habits.html`, Q3 ("solving problems that have no
obvious correct answer"), Q9 ("independence and freedom"), and Q12 ("unique
ideas or solutions") are all positively-worded — reverse-scoring them (as an
earlier version of this pipeline did) was a mistake. The one genuinely
reverse-worded item is Q6, "the tasks on the job are simple and uncomplicated"
— which also matches the reverse item in the Work Design Questionnaire this
survey is adapted from. Only Q6 is reverse-scored below.

Creative Perceptions reverse items (Q6, Q11) were checked against
`creative-perceptions.html` and are worded as expected — unchanged.

```{r recode-likert}
kai_levels <- c("Very Hard" = 1, "Hard" = 2, "Easy" = 3, "Very Easy" = 4)
agree_levels <- c("Strongly Disagree" = 1, "Disagree" = 2,
                   "Neither Agree nor Disagree" = 3, "Agree" = 4,
                   "Strongly Agree" = 5)

recode_likert <- function(x, levels) unname(levels[x])

scored_data <- analysis_sample %>%
  mutate(across(matches("^kaiSurvey_Q\\d+$"), ~ recode_likert(.x, kai_levels))) %>%
  mutate(across(matches("^creativePerceptions_Q\\d+$"), ~ recode_likert(.x, agree_levels))) %>%
  mutate(across(matches("^workHabits_Q\\d+$"), ~ recode_likert(.x, agree_levels)))
```

```{r reverse-score}
reverse_cols <- c(
  "creativePerceptions_Q6", "creativePerceptions_Q11",
  "workHabits_Q6"
)

scored_data <- scored_data %>%
  mutate(across(all_of(reverse_cols), ~ 6 - .x))
```

```{r average-scores}
scored_data <- scored_data %>%
  mutate(
    kai_score = rowMeans(pick(matches("^kaiSurvey_Q\\d+$")), na.rm = TRUE),
    creative_perceptions_score = rowMeans(pick(matches("^creativePerceptions_Q\\d+$")), na.rm = TRUE),
    work_habits_score = rowMeans(pick(matches("^workHabits_Q\\d+$")), na.rm = TRUE)
  )

scored_data <- scored_data %>%
  left_join(b5_scored, by = "participant_id")

scored_data %>%
  select(participant_id, kai_score, creative_perceptions_score, work_habits_score,
         Extraversion, Agreeableness, Conscientiousness, EmotionalStability, Openness)
```

## Step 9: Composite Survey Score

Pre-registered secondary test (a): equal-weight mean of z-scored Creative
Perceptions, Work Habits, and KAI, computed within this analysis sample (will
restabilize as more participants are collected).

```{r survey-score}
scored_data <- scored_data %>%
  mutate(
    SurveyScore = rowMeans(
      cbind(
        scale(creative_perceptions_score)[, 1],
        scale(work_habits_score)[, 1],
        scale(kai_score)[, 1]
      ),
      na.rm = TRUE
    )
  )

scored_data %>% select(participant_id, creative_perceptions_score, work_habits_score, kai_score, SurveyScore)
```

## Step 10: Psychological richness (Three Good Lives)

The Three Good Lives instrument has 15 items (only collected from participants
20-24 onward — `NA` for 7-10). Its "psychologically rich life" subscale isn't
explicitly keyed anywhere in this repo, so the grouping below is **inferred
from item wording** rather than a verified published key: `interesting,
dramatic, psychologically_rich`, plus reverse-scored `uneventful, monotonous`
(1-7 scale, reverse = `8 - x`). Treat with appropriate caution — it's used
purely exploratorily per the pre-registration.

```{r psych-richness}
scored_data <- scored_data %>%
  mutate(across(matches("^threeGoodLife_tgl_"), extract_paren_num)) %>%
  mutate(
    PsychRichness = rowMeans(
      cbind(
        threeGoodLife_tgl_interesting,
        threeGoodLife_tgl_dramatic,
        threeGoodLife_tgl_psychologically_rich,
        8 - threeGoodLife_tgl_uneventful,
        8 - threeGoodLife_tgl_monotonous
      ),
      na.rm = TRUE
    )
  )

scored_data %>% select(participant_id, PsychRichness, creative_perceptions_score)
```

Pre-registered exploratory correlation: does psychological richness correlate
with Creative Perceptions? (n=5 — only participants 20-24 have this measure.)

```{r psych-richness-correlation}
pr_cor_data <- scored_data %>%
  filter(!is.nan(PsychRichness))

cor.test(pr_cor_data$PsychRichness, pr_cor_data$creative_perceptions_score)
```

```{r write-scores}
write_csv(
  scored_data %>%
    select(participant_id, kai_score, creative_perceptions_score, work_habits_score,
           SurveyScore, PsychRichness, Extraversion, Agreeableness, Conscientiousness,
           EmotionalStability, Openness),
  "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/survey_scores.csv"
)
```

## Step 11: Face-level covariates (age, sex)

`PetersonFaceData.csv` lists each face stimulus once (plus a duplicate
"(Repeat)" row for the 10 repeat faces, carrying no extra information).
`FaceAge` is the face's mean estimated age, grand-mean-centered across the
faces used in this analysis. `FaceSex` isn't directly labeled, but the
norming data's continuous `gender` column (0-100) splits cleanly into 6
Male / 6 Female per age bracket at `gender > 50` — matching the pre-registered
"six male and six female faces per bracket" design — so that threshold is used
to derive it.

```{r read-peterson}
peterson_data <- read_csv(
  "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/PetersonFaceData.csv",
  show_col_types = FALSE
) %>%
  filter(!str_detect(Bucket, "Repeat")) %>%
  mutate(Stimulus = as.character(Stimulus)) %>%
  distinct(Stimulus, `Mean Age`, gender) %>%
  transmute(
    face_num = Stimulus,
    FaceAge_raw = `Mean Age`,
    FaceSex = if_else(gender > 50, "Male", "Female")
  )

face_covariates <- peterson_data %>%
  mutate(FaceAge = FaceAge_raw - mean(FaceAge_raw, na.rm = TRUE)) %>%
  select(face_num, FaceAge, FaceSex)

face_covariates
```

## Step 12: Trial-level long dataset for the mixed models

One row per participant x first-presentation face (9 participants x 60 faces),
joining rating, face covariates, condition, survey scores, and available
demographics. `NA` where a field doesn't exist for that participant's survey
version (political orientation, education, SES, and PsychRichness are only
available for participants 20-24).

```{r trial-long}
trial_data <- face_long %>%
  left_join(face_covariates, by = "face_num") %>%
  left_join(
    scored_data %>%
      select(participant_id, condition, kai_score, creative_perceptions_score,
             work_habits_score, SurveyScore, PsychRichness,
             Extraversion, Agreeableness, Conscientiousness, EmotionalStability, Openness,
             ParticipantAge = demographics_age, ParticipantSex = demographics_sex,
             ParticipantRace = demographics_race,
             Education = demographics_educationLevel,
             SES = demographics_socialStatusLadder,
             PoliticalEconomic = demographics_politicalEconomic,
             PoliticalSocial = demographics_politicalSocial),
    by = "participant_id"
  ) %>%
  mutate(
    Participant = factor(participant_id),
    Face = factor(face_num),
    FaceSex = factor(FaceSex),
    CreativePerceptions = creative_perceptions_score,
    WorkHabits = work_habits_score,
    KAI = kai_score
  )

nrow(trial_data)  # expect 9 * 60 = 540
```

## Step 13: Mixed-model fitting with the pre-registered fallback ladder

Per the pre-registration: if a model fails to converge, first drop the
random-slope correlation, then drop the random slope, reporting all attempted
specifications.

```{r fit-helper}
fit_with_fallback <- function(fixed_rhs, data, label) {
  specs <- list(
    full = paste0("rating ~ ", fixed_rhs, " + (1 + FaceAge | Participant) + (1 | Face)"),
    no_slope_corr = paste0("rating ~ ", fixed_rhs, " + (1 + FaceAge || Participant) + (1 | Face)"),
    no_slope = paste0("rating ~ ", fixed_rhs, " + (1 | Participant) + (1 | Face)")
  )

  attempts <- list()
  for (spec_name in names(specs)) {
    formula_str <- specs[[spec_name]]
    # lme4/lmerTest resolve `data` via match.call() + parent-frame lookups;
    # under knitr's evaluate() that extra stack depth can make it look up the
    # wrong frame (fails with "object '<outer var name>' not found"). Passing
    # the data via do.call() embeds the already-evaluated data frame directly
    # into the call, leaving no symbol for that lookup to get wrong.
    fit <- withCallingHandlers(
      tryCatch(
        do.call(lmer, list(formula = as.formula(formula_str), data = data, REML = TRUE)),
        error = function(e) e
      ),
      warning = function(w) invokeRestart("muffleWarning")
    )
    converged <- !inherits(fit, "error") &&
      (is.null(fit@optinfo$conv$lme4$code) || length(fit@optinfo$conv$lme4$code) == 0) &&
      !isSingular(fit)
    attempts[[spec_name]] <- list(formula = formula_str, fit = fit, converged = converged)
    if (converged) break
  }

  chosen_name <- names(attempts)[length(attempts)]
  chosen <- attempts[[chosen_name]]
  cat("[", label, "] specification used:", chosen_name,
      "| converged cleanly:", chosen$converged, "\n")
  cat("    formula:", chosen$formula, "\n")

  list(label = label, spec_used = chosen_name, formula = chosen$formula,
       converged = chosen$converged, fit = chosen$fit, attempts = attempts)
}

tidy_or_note <- function(model_result) {
  if (inherits(model_result$fit, "error")) {
    tibble(model = model_result$label, term = NA_character_,
           note = paste("failed to fit:", conditionMessage(model_result$fit)))
  } else {
    broom.mixed::tidy(model_result$fit, effects = "fixed") %>%
      mutate(model = model_result$label, spec_used = model_result$spec_used, .before = 1)
  }
}
```

### Primary confirmatory test (professional-advice condition)

`Rating ~ FaceAge × CreativePerceptions + Big5 + FaceSex + (1 + FaceAge |
Participant) + (1 | Face)`. All 9 pilot participants are in the professional
condition, so this is the full pilot sample.

```{r model-primary}
model_primary <- fit_with_fallback(
  "FaceAge * CreativePerceptions + Extraversion + Agreeableness + Conscientiousness + EmotionalStability + Openness + FaceSex",
  trial_data, "primary_confirmatory"
)
```

### Domain-specificity test — not fit yet

Pre-registered formula: `Rating ~ Condition × FaceAge × CreativePerceptions +
FaceSex + (1 + FaceAge | Participant) + (1 | Face)`, fit on professional +
emotional conditions pooled. **Not fit here** — all 9 pilot participants are in
the `professional` condition, so `Condition` has no variation to test yet.
Ready to run once emotional-condition data is collected.

### Secondary confirmatory tests

(a) Composite Survey Score replacing Creative Perceptions:

```{r model-secondary-surveyscore}
model_secondary_surveyscore <- fit_with_fallback(
  "FaceAge * SurveyScore + Extraversion + Agreeableness + Conscientiousness + EmotionalStability + Openness + FaceSex",
  trial_data, "secondary_survey_score"
)
```

(b) Work Habits and KAI, each as separate models:

```{r model-secondary-workhabits}
model_secondary_workhabits <- fit_with_fallback(
  "FaceAge * WorkHabits + Extraversion + Agreeableness + Conscientiousness + EmotionalStability + Openness + FaceSex",
  trial_data, "secondary_work_habits"
)
```

```{r model-secondary-kai}
model_secondary_kai <- fit_with_fallback(
  "FaceAge * KAI + Extraversion + Agreeableness + Conscientiousness + EmotionalStability + Openness + FaceSex",
  trial_data, "secondary_kai"
)
```

### Mechanism probe — not fit yet

Pre-registered as the primary model fit within the perceived-intelligence
condition. **Not fit here** — no `intelligence`-condition data exists yet.

### Exploratory model

`Rating ~ FaceAge × CreativePerceptions + Big5 + PsychRichness + ParticipantAge
+ ParticipantSex + ParticipantRace + Education + SES + PoliticalOrientation +
FaceSex + (1 + FaceAge | Participant) + (1 | Face)`. Several of these terms
(`PsychRichness`, `Education`, `SES`, political-orientation items) only exist
for participants 20-24, so this effectively runs on n=5, not n=9 — `lmer` drops
any row with a missing predictor.

```{r model-exploratory}
model_exploratory <- fit_with_fallback(
  paste(
    "FaceAge * CreativePerceptions",
    "+ Extraversion + Agreeableness + Conscientiousness + EmotionalStability + Openness",
    "+ PsychRichness + ParticipantAge + ParticipantSex + Education + SES",
    "+ PoliticalEconomic + PoliticalSocial + FaceSex"
  ),
  trial_data, "exploratory"
)
```

### Combined results table

```{r combined-results}
all_models <- list(model_primary, model_secondary_surveyscore,
                    model_secondary_workhabits, model_secondary_kai,
                    model_exploratory)

model_results <- map_dfr(all_models, tidy_or_note)
model_results
```

```{r write-model-results}
write_csv(
  model_results,
  "/Users/isaaccohen/fastapi-jspsych-experiment-template-public-1/exported_data/model_results.csv"
)
```

## Caveats

- **n = 9 of a planned 600.** Random-effect variance components, convergence
  behavior, and fixed-effect estimates above are pilot-scale sanity checks on
  the pipeline, not evidence for or against H1/H2.
- The domain-specificity and mechanism-probe tests require condition variation
  this batch doesn't have yet.
- `PsychRichness` and several exploratory demographic covariates are only
  available for participants 20-24 (n=5), since those fields were added to the
  survey after participants 7-10 took part.
- The bot-check/attention-check exclusion criterion can't be evaluated from
  stored data, since the front end already blocks submission on failure.
